# **Loading and preprocessing the data**

## Load the data

```{r, echo = TRUE}
activity_data <- read.csv("activity.csv")
```

## Process/transform the data (if necessary) into a format suitable for your analysis

```{r, echo = TRUE}
activity_data$date <- as.Date(activity_data$date, "%m/%d/%Y")
str(activity_data)
head(activity_data)
```

# **What is mean total number of steps taken per day?**

## Calculate the total number of steps taken per day

```{r, echo = TRUE}
StepsPerDay <- aggregate(steps ~ date, data = activity_data, sum, na.rm = TRUE)
str(StepsPerDay)
head(StepsPerDay)
```

## Make a histogram of the total number of steps taken each day

```{r, echo = TRUE}
library(ggplot2)
p <- qplot(x = date, y = steps, data = StepsPerDay, geom = "histogram", 
        stat = "identity")
p + labs(title = "Total Steps Per Day", x = "Day", y = "Steps")
```

## Calculate and report the mean and median of the total number of steps taken per day

### Mean steps per day:
```{r, echo = TRUE}
round(mean(StepsPerDay$steps))
```

### Median steps per day:
```{r, echo = TRUE}
round(median(StepsPerDay$steps))
```

# **What is the average daily activity pattern?**

## Make a time series plot of the 5-minute interval and the average number
## of steps taken, averaged across all days

```{r, echo = TRUE}
time_series <- aggregate(steps ~ interval, data = activity_data, mean, na.rm = TRUE)
plot(time_series$interval, time_series$steps,
        type = "l",
        col = "blue",
        main = "Average Steps Taken Per 5-minute Interval Across All Days",
        xlab = "5-minute Interval",
        ylab = "Average Number of Steps Taken")
```

## Which 5-minute interval, on average across all the days in the dataset,
## contains the maximum number of steps?

```{r, echo = TRUE}
max_interval_steps <- which.max(time_series$steps)
time_series[max_interval_steps, ]
```

# **Imputing Missing Values**

## Calculate and report the total number of missing values in the dataset (i.e. NA's)

```{r, echo = TRUE}
activity_data_NA <- sum(is.na(activity_data))
activity_data_NA
```

## Devise a strategy for filling in all of the missing values in the dataset
## (strategy is to replace NA's with the mean for that 5-minute interval)

```{r, echo = TRUE}
new_data_fill <- activity_data
for(i in 1:nrow(new_data_fill)){
        if(is.na(new_data_fill$steps[i])){
                corresponding_interval <- new_data_fill$interval[i]
                time_series_row <- which(time_series$interval == corresponding_interval)
                new_steps <- time_series$steps[time_series_row]
                new_data_fill$steps[i] <- new_steps
        }
}
```

## Create a new dataset that is equal to the original dataset, but with the missing
## data filled in

```{r, echo = TRUE}
head(new_data_fill)
tail(new_data_fill)
```

## Make a histogram of the total number of steps taken each day, and calculate and
## report the mean and medial total number of steps taken per day

```{r, echo = TRUE}
New_StepsPerDay <- aggregate(steps ~ date, data = new_data_fill, sum, na.rm = TRUE)
str(New_StepsPerDay)
head(New_StepsPerDay)

p2 <- qplot(x = date, y = steps, data = New_StepsPerDay, geom = "histogram", 
           stat = "identity")
p2 + labs(title = "Total Steps Per Day", x = "Day", y = "Steps")

round(mean(New_StepsPerDay$steps))
round(median(New_StepsPerDay$steps))
```

### Do these values differ from the estimates from the first part of the assignment?

### What is the impact of imputing missing data on the estimates of the total daily
### number of steps?