# **Loading and preprocessing the data**

## Load the data

```{r, echo = TRUE}
activity_data <- read.csv("activity.csv")
```

## Process/transform the data (if necessary) into a format suitable for your analysis

```{r, echo = TRUE}
activity_data$date <- as.Date(activity_data$date, "%m/%d/%Y")
str(activity_data)
head(activity_data)
```

# **What is mean total number of steps taken per day?**

## Calculate the total number of steps taken per day

```{r, echo = TRUE}
StepsPerDay <- aggregate(steps ~ date, data = activity_data, sum, na.rm = TRUE)
str(StepsPerDay)
head(StepsPerDay)
```

## Make histogram of the total number of steps taken each day

```{r, echo = TRUE}
library(ggplot2)
p <- qplot(x = date, y = steps, data = StepsPerDay, geom = "histogram", 
        stat = "identity")
p + labs(title = "Total Steps Per Day", x = "Day", y = "Steps")
```

## Calculate and report the mean and median of the total number of steps taken per day

### Mean steps per day:
```{r, echo = TRUE}
round(mean(StepsPerDay$steps))
```

### Median steps per day:
```{r, echo = TRUE}
round(median(StepsPerDay$steps))
```

